Digital Addiction

### 2024-02-15 paper/paper.qmd
add reference

>>>>

Our paper is followed by a reproduction of Hunt Allcott, Matthew Gentzkow, and Lena Song’s analysis[@originalpaper] of digital addiction to social media and their experiments prove reducing the usage of social media incentive new habits. Furthermore, their model shows that self-control is one of the important problems for people and it causes 31 percent of social media use.
